---
title: "tech workshop markdown example"
author: "Shaun Bartschi"
date: "2025-06-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Example

# Getting Started

First, call our library
```{r, message = FALSE}
library(tidyverse)
```

Now plot the relationship between horsepower and mpg for cars in the mtcars dataset (which is a dataset internal to R). Show a local regression smooth, along with the linear model estimate. 

```{r}
ggplot(mtcars, aes(x = hp, y = mpg)) + 
  geom_point() + 
  geom_smooth(se = FALSE, method = 'loess', formula = 'y ~ x') +
  geom_smooth(se = FALSE, method = "lm", col = "red", formula = 'y ~ x')
```


```{r}
# The trend is not very linear, but for simplicity, lets assume that it is 
# "linear-ish". Fit a linear model and obtain the coeffcients of the model
# that uses horsepower to predict fuel economy. 
tlm <- lm(mpg ~ hp, data = mtcars)
summary(tlm)
```



```{r}
# Use LaTeX to create a model that has the following form
# y_hat = b_0 + b_1*h_p
# where b_0 and b_1 are the model coefficients. 

# Knit the results to pdf to see if your equation rendered properly.
```
\[
     \hat{y} = b_0 + b_1\cdot h_p
\]
where \(b_0\) and \(b_1\) are the model coefficients.  Using values from our regression, we get

\[
     \hat{y} = `r tlm$coefficients[1]` + `r tlm$coefficients[2]` \cdot h_p
\]